---
title: "Alliance Inpatient Daily Census"
subtitle: "TBD"
author: 
  name: "John Ryan Kivela, MA"
  email: "Ryan.Kivela@narbha.org"
date: today
date-format: long
format:
  html:
    theme: pulse
    embed-resources: true
    toc: true
    toc-depth: 6
    code-fold: true
    footnotes-hover: true
---

# Setup

```{r}
#| label: Setup
#| eval: true
#| include: false
#| echo: false
#| warning: false
#| error: false

## Load Libraries
 library(fs)
# library(purrr)
# library(readxl)
 library(tidyverse)
# library(lubridate)

DWPROD01 <- DBI::dbConnect(odbc::odbc(), "BehavioralHealthAlliance")

```

# Enrollment Roster

Import the most recent enrollment roster. The Alliance Member Enrollment Roster is generated monthly as a part of the Alliance Progress Report.

```{r}
#| label: Alliance Member Enrollment Roster
#| eval: true
#| include: true
#| echo: true
#| warning: false
#| error: false

# Import the data from the monthly Alliance Progress Report
AllianceMemberEnrollmentRoster <- read.csv("./data/ActiveNAZMembership.csv")

AllianceMemberEnrollmentRoster <-
  AllianceMemberEnrollmentRoster |> 
  select(
    -SpokenLanguage,
    #-EmploymentStatus,
    -MilitaryStatus
  )

```

# Health Choice Daily Census Files

Run SQL on HC SQL server and import the files here. There is one file each for the Inpatient Census and the Discharge Census. The CSV from the SQL query from HCA comes in with no column headers, so those must be assigned.

The census file is then combined with the enrollment roster to form a complete tool for the provider.

```{r}
#| label: HCA Daily inpatient census import
#| eval: true
#| include: true
#| echo: true
#| warning: false
#| error: false

AllianceInpatientCensus <- read.csv("./data/Input/CensusInpatient.csv")

colnames(AllianceInpatientCensus) <- c("SourceSystem", 
                                       "BuildVersion", 
                                       "LastName", 
                                       "MiddleInitial",
                                       "FirstName",
                                       "MemberID",
                                       "PhoneNumber",
                                       "AdmissionDate",
                                       "LOS",
                                       "Facility",
                                       "FacilityType",
                                       "StayType",
                                       "AdmittingDiagnosisCode",
                                       "AdmittingDiagnosisDescription",
                                       "AdmissionAuthorizationIndicator",
                                       "BuildDate"
                                       )

```

```{r}
#| label: HCA Daily discharge census import
#| eval: true
#| include: true
#| echo: true
#| warning: false
#| error: false

AllianceDischargeCensus <- read.csv("./data/Input/CensusDischarge.csv")

colnames(AllianceDischargeCensus) <- c("SourceSystem",
                                       "BuildVersion", 
                                       "LastName",
                                       "MiddleInitial",
                                       "FirstName",
                                       "MemberID",
                                       "AdmissionDate",
                                       "DischargeDate",
                                       "LOS",
                                       "DischargeDisposition",
                                       "Facility",
                                       "FacilityType",
                                       "StayType",
                                       "AdmittingDiagnosisCode",
                                       "AdmittingDiagnosisDescription",
                                       "DischargeDiagnosisCode",
                                       "DischargeDiagnosisDescription",
                                       "AdmissionAuthorizationIndicator",
                                       "BuildDate"
                                       )
```

```{r}
#| label: Merge Census Files
#| eval: true
#| include: true
#| echo: true
#| warning: false
#| error: false

AllianceDailyInpatientCensus <-
  merge(x = AllianceInpatientCensus,
        y = AllianceDischargeCensus,
        by = c("LastName", "FirstName", "AdmissionDate", "Facility"),
        all.x = TRUE)
```

```{r}
#| label: Select variable and calc LOS
#| eval: true
#| include: true
#| echo: true
#| warning: false
#| error: false

# Create AHCCCSID from MemberID
AllianceDailyInpatientCensus$AHCCCSID <- substr(AllianceDailyInpatientCensus$MemberID.x, 4, nchar(AllianceDailyInpatientCensus$MemberID.x))

# Select Variables
AllianceDailyInpatientCensus <-
  AllianceDailyInpatientCensus |> 
  select(
    AHCCCSID,
    LastName,
    FirstName,
    Facility,
    AdmissionDate,
    DischargeDate,
    DischargeDisposition,
    #FacilityType.x,
    #StayType.x
  )

# Calculate LOS
AllianceDailyInpatientCensus$AdmissionDate <- as.Date(AllianceDailyInpatientCensus$AdmissionDate)
AllianceDailyInpatientCensus$DischargeDate <- as.Date(AllianceDailyInpatientCensus$DischargeDate)

AllianceDailyInpatientCensus$LengthofStay <-
  (AllianceDailyInpatientCensus$DischargeDate - AllianceDailyInpatientCensus$AdmissionDate)
```

```{r}
#| label: combine with enrollment roster
#| eval: true
#| include: true
#| echo: true
#| warning: false
#| error: false

# Merge tables
AllianceDailyInpatientCensus <-
  merge(x = AllianceDailyInpatientCensus,
        y = AllianceMemberEnrollmentRoster,
        by = "AHCCCSID",
        all.x = TRUE)

# Rename some columns
AllianceDailyInpatientCensus <-
  AllianceDailyInpatientCensus |> 
  rename(
    LastName = "LastName.x",
    FirstName = "FirstName.x",
    #FacilityType = "FacilityType.x",
    #StayType = "StayType.x"
  ) |> 
  select(
    -X, 
    -FirstName.y,
    -LastName.y,
    -DOD
  )

# Remove duplicates
AllianceDailyInpatientCensus <-
  AllianceDailyInpatientCensus |> 
  distinct(
    AHCCCSID,
    LastName,
    AdmissionDate,
    .keep_all = TRUE
  )

# Arrange by Admit date and AHCCCSID
AllianceDailyInpatientCensus <-
  AllianceDailyInpatientCensus |> 
  arrange(desc(AdmissionDate), AHCCCSID)

# Write to CSV
write.csv(AllianceDailyInpatientCensus,"./data/Output/AllianceDailyInpatientCensus.csv")

```

# Distribute Data

The overall Alliance Daily Inpatient Census is split according to Alliance Provider, and saved to their respective intranet folders.

```{r}
# Create a directory to store the CSV files
data_dir <- "./data/output"
dir.create(data_dir, showWarnings = FALSE)

# Split the data frame based on AllianceProviderShortname
split_data <- split(AllianceDailyInpatientCensus, AllianceDailyInpatientCensus$BHHShortName)

# Iterate over the list and save each data frame as a separate CSV file in the corresponding folder
for (provider_name in names(split_data)) {
  provider_data <- split_data[[provider_name]]
  folder_name <- file.path(data_dir, provider_name)
  dir.create(folder_name, showWarnings = FALSE)
  file_name <- file.path(folder_name, paste0("AllianceDailyInpatientCensus_", provider_name, ".csv"))
  write.csv(provider_data, file = file_name, row.names = FALSE)
}
```











